\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Aadel Asad} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 92-315-4333909 ~ \href{mailto:aadel.sheikh34@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{aadel.sheikh34@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/aadel-asad/}{\raisebox{-0.2\height}\faLinkedin\ \underline{aadel-asad}}  ~
    \href{https://github.com/aa-del9}{\raisebox{-0.2\height}\faGithub\ \underline{aa-del9}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Science and Technology}{Sep. 2022 -- Present}
      {Bachelor of Science in Computer Science}{Islamabad, Pakistan}
  \resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
    {Oryns Solutions Pvt. Ltd.}{June 2024 -- Present}
    {FrontEnd Lead}{Self-employed}
    \resumeItemListStart
      \resumeItem{Leading the frontend team developing multiple client apps using React and React Native.}
      \resumeItem{Architecting and optimizing frontend codebase, ensuring scalability and performance.}
      \resumeItem{Collaborating with designers, product managers, and backend teams for seamless UI/UX.}
      \resumeItem{Conducting code reviews, mentoring, and best practice implementation.}
       \resumeItem{Implementing CI/CD pipelines, automated testing, and performance optimizations.}
    \resumeItemListEnd
\resumeSubheading
    {Parhlai! – (An Entry Test Preparation App)}{April 2024 -- Present}
    {Technical Lead}{Self-employed}
    \resumeItemListStart
      \resumeItem{Leading a full-stack development team, while managing both frontend (Next.js) and backend (ExpressTS) development.}
      \resumeItem{Utilizing industry best practices for project & team management, including Jira and Confluence.}
      \resumeItem{Architecting scalable solutions, ensuring adherence to best practices 
& DevOps principles, including IAC setup with Terraform, CI/CD setup
with GitHub Actions & AWS services including EC2, S3, ECR, Cognito.}
    \resumeItemListEnd

\resumeSubheading
    {Cognizance Solutions Pvt. Ltd.}{March 2024 -- Sep. 2024}
    {Full Stack Developer}{Remote}
    \resumeItemListStart
      \resumeItem{Leading a full-stack development team, while managing both frontend (Next.js) and backend (ExpressTS) development.}
      \resumeItem{Utilizing industry best practices for project & team management, including Jira and Confluence.}
      \resumeItem{	Architecting scalable solutions, ensuring adherence to best practices 
& DevOps principles, including IAC setup with Terraform, CI/CD setup
with GitHub Actions & AWS services including EC2, S3, ECR, Cognito.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-10pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
  {\textbf{Bill Splitting App} $|$ \emph{React Native, Express, MongoDB}}{}
  \resumeItemListStart
    \resumeItem{Built a full-stack mobile app for simplified bill splitting using React Native (Expo), Node.js, Express, and MongoDB.}
    \resumeItem{Designed secure authentication with JWT and developed REST APIs for expense tracking, group management, and settlement.}
  \resumeItemListEnd
 \vspace{-13pt}
\resumeProjectHeading
  {\textbf{Mock Interview Platform} $|$ \emph{Next.js, ShadCN UI}}{}
  \resumeItemListStart
    \resumeItem{Contributed to frontend development of an AI-driven mock interview platform using Next.js and ShadCN UI.}
    \resumeItem{Developed reusable components, handled authentication workflows, and integrated API routes for user metrics.}
    \resumeItem{Ensured performant client-side rendering and optimized for mobile responsiveness.}
  \resumeItemListEnd
 \vspace{-13pt}
\resumeProjectHeading
  {\textbf{Telehealth Platform} $|$ \emph{Next.js, Node.js, WebSockets, ShadCN UI}}{}
  \resumeItemListStart
    \resumeItem{Developed a Blockchain-secured and scalable telehealth web application with real-time consultations via Web-RTC (p2p video-calling).}
    \resumeItem{Implemented GDPR-compliant workflows, patient-doctor scheduling, encrypted messaging, and role-based dashboards.}
    \resumeItem{Supported CI/CD pipelines and serverless deployment.}
  \resumeItemListEnd
 \vspace{-13pt}
\resumeProjectHeading
  {\textbf{Silent Speech} $|$ \emph{Kotlin, MediaPipe, TensorFlow Lite}}{}
  \resumeItemListStart
    \resumeItem{Built an Android app for real-time sign language recognition using MediaPipe and TensorFlow Lite.}
    \resumeItem{Classified over 400,000 hand gesture samples across 51 ASL classes with optimized on-device inference.}
    \resumeItem{Integrated responsive camera pipeline for smooth user experience and asynchronous gesture detection.}
    \resumeItem{Focused on seamless ML integration within mobile constraints.}
  \resumeItemListEnd
 \vspace{-13pt}
\resumeProjectHeading
  {\textbf{Prison Management System} $|$ \emph{Python, Tkinter, Pandas, bcrypt}}{}
  \resumeItemListStart
    \resumeItem{Built desktop system to manage prisoner and staff records including attendance and medical logs.}
    \resumeItem{Used Pandas for structured CSV data handling and implemented secure role-based access with bcrypt.}
    \resumeItem{Designed CRUD workflows, integrated search/filtering, and ensured reliable data persistence with validation.}
  \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{FrontEnd}{: NextJS, React.js, TypeScript, Redux, TailwindCSS, Bootstrap, HTML, CSS} \\
     \textbf{BackEnd}{: Python, Flask, Node.js, ExpressTS, MongoDB, Mongoose, MySQL, PostgreSQL, DynamoDB} \\
     \textbf{DevOps}{: AWS: (EC2, S3, Cloudfront, ECR, Lambda), Terraform, Docker, Github Actions.} \\
     \textbf{Soft skills}{: Time management, Effective communication, Teamwork.} \\
    }}
 \end{itemize}


% %-----------INVOLVEMENT---------------
% \section{Leadership / Extracurricular}
%     \resumeSubHeadingListStart
%         \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
%             \resumeItemListStart
%                 \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
%                 \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
%                 \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
%             \resumeItemListEnd
        
%     \resumeSubHeadingListEnd


\end{document}
